\begin{tabu}{X X[7]}    
    Title & \large Software-Defined Wireless Sensor Networks (SDWSN) \\[.5ex]

    Description& \small This project brings \textbf{Software-Defined Networking (SDN)} concepts in to \textbf{Wireless Sensor Networks (WSNs)}. A \textbf{Client-Server} model connects each separated WSN to a \textbf{Centralized Controller} located in the Server. Client program exposes \textbf{REST} APIs to access Controller's resources. A \textbf{Single Page Application (SPA)} written in javascript \textbf{(Angularjs)} is in charge of monitoring the whole network.\normalsize\\&\\
    Significance & 
    \small\textbullet~Highly modular and loosely coupled design, written in Java.\normalsize\\&
    \small\textbullet~Cetralized Controller and Database.\normalsize\\&
    \small\textbullet~Clean and robust code; more than 200 unit tests with code coverage up to 80 percent\normalsize
\end{tabu}

\begin{tabu}{X X[7]}    
    Title & \large Motion Controlled Robotic Arm\\[.5ex]
    Description & \small A \textbf{servo robotic arm} which is controlled by analyzing potentiometer sensors signals attached to human arm. The system utilizes an \textbf{ARM Cortex-M3} board running \textbf{uC/OS-II}. Fixed number of real-time processes are executing controll algorithms.\normalsize\\&\\
    Significance &
    \small\textbullet~Enhance existing MATLAB controll procedures and algorithms to C code\normalsize\\&
    \small\textbullet~Design and create a prototype of the system\normalsize\\&
    \small\textbullet~Real-Time task scheduler with uC/OS-II\normalsize
\end{tabu}

\begin{tabu}{X X[7]}    
    Title & \large CAN Controller Module\\[.5ex]
    Description & \small This project provides an expandable communication interface in order to add/remove floors to an existing elevator controll board. The main bord communicates with different modules via CAN protocol.\normalsize\\&\\
    Significance &
    \small\textbullet~Cost-effective and maintainable solution for expandign current elevator infrastructure\normalsize\\&
    \small\textbullet~Using \textbf{MCP2515} CAN Controller with \textbf{MCP2552} CAN Tranceiver\normalsize\\&
    \small\textbullet~Using \textbf{PIC18F} microcontroller to drive CAN protocol and communicate with controller board\normalsize
\end{tabu}
